Relationships in the extremes and their influence on competition and coexistence: Supporting information

### 2022-01-26 paper/SupMat.Rnw
SM model setup

%***DAN: Jasmin, please start on this section when you get a chance. Here are some topics that need
%to be covered:

@@

>>>>

%***DAN: Jasmin, please start on this section when you get a chance. Here are some topics that need
%to be covered:
Estimations of $Q_i(t)$, $V_i(t)$, and $K_i(t)$, temperature dependence functions for cell quota, reproduction rate, and half saturation, respectively, were used to paramaterize the competing diatom model outline in the paper. 
Values of and subsequent function estimations are plotted in Figure \ref{fig:VQK}. 
Descamps and Julien obtained estimated values for $Q_i$, $V_i$, and $K_i$ from single species nine-day batch experiments at four different temperatures (6, 12, 18, 24) (see Table 1 of Descamps and Julien) and further computed a linear interpolation to define temperature dependence functions of $Q_i(t)$, $V_i(t)$, and $K_i(t)$. These values and functions are indicated in Figure \ref{fig:VKQ} by open circles and dashed lines. Ellner 2016 and 2019 chose to slightly modify some values and functions, indicated in Figure \ref{fig:VKQ} by closed circles and solid lines.

@@

\begin{figure}
\includegraphics[width=.66\textwidth]{../results_figs/VKQfig.pdf}
\caption[caption]
{caption \label{fig:VKQ}}
\end{figure}
